### 2019-05-03 README.Rmd
README
explain sub-projects in README

**title**

@@

@@

@@

# Runtime

Predicted total runtime.
The time is based on all targets that have been created so far in the project.
Estimated time will differ depending on the CPU speed and possible availability of a HPC.

```{r README-2 }
r_predict_runtime()
```

>>>>

**Modeling defoliation as a proxy for tree health: Comparison of feature-selection methods across multiple feature sets derived from hyperspectral data**

@@

## Paper

@@

The following directories belong to this project

- `analysis/01-download.R`
- `analysis/02-hyperspectral-processing.R`
- `analysis/04-data-processing.R`
- `analysis/05-modeling/`

## Other Content

In addition, it contains the workflow for a sub-project: Predicting defoliation to the Basque Country (for the years 2017 and 2018) using Sentinel-2 data.

The following "targets" are important for this sub-project:

- `defoliation_raster` (in `analysis/03-sentinel-processing`)

@@
